Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine comoving star pairs from low-resolution spectroscopic follow-up

### 2017-06-01 paper/comoving-followup.tex
caption

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.9\linewidth]{sample_cmd.pdf}
  \end{center}
  \caption{%
    \todo{Stuff}
    \label{fig:sample-cmd}}
\end{figure}

@@

This work is based on observations obtained at the MDM Observatory, operated by
Dartmouth College, Columbia University, Ohio State University, Ohio University,
and the University of Michigan.
% The authors are pleased to acknowledge that the work reported on in this paper
% was substantially performed at the TIGRESS high performance computer center at
% Princeton University which is jointly supported by the Princeton Institute for
% Computational Science and Engineering and the Princeton University Office of
% Information Technology's Research Computing department.

\software{
The code used in this project is available from
\url{https://github.com/adrn/GaiaPairsFollowup} under the MIT open-source
software license.
This research utilized the following open-source \python\ packages:
    \package{Astropy} (\citealt{Astropy-Collaboration:2013}),
    \package{astroquery} (\citealt{Ginsburg:2016}),
    \package{ccdproc} (\citealt{Craig:2015}),
    \package{celerite} (\citealt{Foreman-Mackey:2017}),
    \package{IPython} (\citealt{Perez:2007}),
    \package{matplotlib} (\citealt{Hunter:2007}),
    \package{numpy} (\citealt{Van-der-Walt:2011}),
    \package{scipy} (\url{https://www.scipy.org/}),
    \package{sqlalchemy} (\url{https://www.sqlalchemy.org/})
}

>>>>

\cite{Gaia-Collaboration:2016,Gaia-Collaboration:2016a}

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.9\linewidth]{sample_cmd.pdf}
  \end{center}
  \caption{%
    Color-magnitude diagram for all \tgas\ sources within $200~\pc$ (blue
    histogram) and all comoving star pair members observed in this follow-up
    effort (black points); lines (orange) connect comoving pairs of stars.
    2MASS $J$-band magnitudes are obtained from the Gaia science
    archive.
    Apparent $G$-band magnitudes (\citealt{Carrasco:2016}) are converted to
    absolute magnitude, $M_G$, using a Lutz-Kelker-corrected
    (\citealt{Lutz:1973}) distance estimate (see also \eqname~1 in
    \citealt{Oh:2017}).
    \label{fig:sample-cmd}}
\end{figure}

@@

This work is based on observations obtained at the MDM Observatory, operated by
Dartmouth College, Columbia University, Ohio State University, Ohio University,
and the University of Michigan.
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by
the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral Agreement.
% The authors are pleased to acknowledge that the work reported on in this paper
% was substantially performed at the TIGRESS high performance computer center at
% Princeton University which is jointly supported by the Princeton Institute for
% Computational Science and Engineering and the Princeton University Office of
% Information Technology's Research Computing department.

\software{
The code used in this project is available from
\url{https://github.com/adrn/GaiaPairsFollowup} under the MIT open-source
software license.
This research utilized the following open-source \python\ packages:
    \package{Astropy} (\citealt{Astropy-Collaboration:2013}),
    \package{astroquery} (\citealt{Ginsburg:2016}),
    \package{ccdproc} (\citealt{Craig:2015}),
    \package{celerite} (\citealt{Foreman-Mackey:2017}),
    \package{IPython} (\citealt{Perez:2007}),
    \package{matplotlib} (\citealt{Hunter:2007}),
    \package{numpy} (\citealt{Van-der-Walt:2011}),
    \package{scipy} (\url{https://www.scipy.org/}),
    \package{sqlalchemy} (\url{https://www.sqlalchemy.org/})
}
This work additionally used the Gaia science archive
(\url{https://gea.esac.esa.int/archive/}).
